Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-23 article.tex
Début rel works

    The resulting method therefore gives a more accurate estimation of the neighbouring relationship than what was proposed before.
\end{abstract}
\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called base station (BS). These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.

@@

    Another method consists in the using the Delauney triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
    [insert Delauney neighbouring reference]

@@

\section{Related works\label{sec:rel_works}}
    \noindent

@@

\section{Contributions\label{sec:contrib}}
    \noindent In section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

@@

        \subsubsection{Distance and angle criterion}
            As seen in section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated. However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.

>>>>

    The resulting method therefore gives a more accurate estimation of the neighbouring relationship than what was proposed before.
\end{abstract}

\begin{IEEEkeywords}
    Neighbours, Telecommunication, Base station, $k$-NN, Adaptative.
\end{IEEEkeywords}

\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known as cells, each of which is supplied by at least one fixed-location transceiver called Base Station (BS). These BSs give the cell network coverage so that voice, data, and other kinds of content may be transmitted.

@@

    Another method consists in the using the Delaunay triangulation. Each couple of points linked by an edge in this triangulation are considered neighbours.
    [insert Delaunay neighbouring reference]

@@

\section{Related works\label{sec:rel_works}}
    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN.

@@

\section{Contributions\label{sec:contrib}}
    \noindent In Section~\ref{sec:overview}, we have seen that we can find the neighbours of BSs by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

@@

        \subsubsection{Distance and angle criterion}
            As seen in Section~\ref{sec:overview}, after having found potential neighbours for each BS, this connexions needs to be filtrated. However, this applies the same distance and angle threshold for all BSs, without taking in account the difference of density.
